Review of Assigned Readings

### 2018-01-02 paper/paper.tex
added my 2 book sources in references.bib and in cited in paper.tex

%************************** Chapters 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyze multiple time series is the VAR (Vector Autoregression) approach. In this approach the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (Lütkepohl, 2005, p. 4-5).\\
To generate the econometric results that follow we used the statistical software STATA.

@@

\subsection{Lag-Specification}
To select the optimal number of lags in our VAR regression we check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (Brandt and Williams, 2007, p. 27). The calculations of these criteria for our given data set are shown in the following table.\\

>>>>

%************************** Chapters 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, we want to examine the underlying relationship between twitter activity and bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyze multiple time series is the VAR (Vector Autoregression) approach. In this approach the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{lütkepohl2007new}).\\
To generate the econometric results that follow we used the statistical software STATA.

@@

\subsection{Lag-Specification}
To select the optimal number of lags in our VAR regression we check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving use the optimal number of lag to use (\cite[p.~27]{brandt_williams_2007}). The calculations of these criteria for our given data set are shown in the following table.\\
